\documentclass{resume}
\begin{document}

  \name{Michael Peterson}

  \info
    {352 Brighton Ave}
    {San Francisco, CA, 94112}
    {(262) 894-8034}
    {http://mpeterson2.github.io/}{mpeterson2.github.io}
    {https://github.com/mpeterson2}{github.com/mpeterson2}
    {mailto:mpeterson418@gmail.com}{mpeterson418@gmail.com}

  \section{Education}
  \begin{tabularx}{\linewidth}{r|X}
    \education{Carthage College}{Kenosha, Wisconsin}{September 2011}{May 2015}{
      Bachelor of Arts Degree in Computer Science
    }
  \end{tabularx}
  \vspace{-2em}

  \section{Work Experience}
  \begin{tabularx}{\linewidth}{r|X}

    \work{Software Engineer}{Blippy}{August 2015}{November 2015}{
      Before the company went out of business, I worked on a small team building a GIF keyboard and organization app for iOS; Used Xcode, writing Objective-C and Swift, to improve and add features to the app; Used Android Studio to start an Android version of the app.
    }

    \work{Software Developer Intern}{Cars.com}{September 2014}{December 2014}{
      Built a web application using the Spring Framework to allow Cars.com developers to query and retrieve images from three separate databases through a single request; worked on the backend team to create a search engine optimized application for vehicle recall information.
    }

    \work{Computer Science Researcher}{North Carolina State University}{June 2014}{August 2014}{
      Researched trust in recommendation systems in order to recommend items to users from their most trusted peers; wrote papers on trust and video capture performance between various different file formats; wrote a web app to help students peer review each other's papers by automatically keeping track of their suggestions with GitHub issues -  \href{http://pdfreviewhub.appspot.com}{pdfreviewhub.appspot.com}
    }

    \work{Tutor/Student Instructor}{Carthage College}{September 2013}{May 2014}{
      Tutored students in computer science classes.
    }

    \work{Software Developer}{Storyteller Software}{June 2013}{December 2013}{
      Recreated the frontend, using Javascript, to create a more maintainable code base; recreated the backend's Java HTTP server to use a RESTful API; introduced the project to other students.
    }

  \end{tabularx}

  \section{Languages and Tools}
    \begin{itemize}
      \item Have substantial experience with Java, JavaScript, Dart and C++.
      \item Have some experience with Swift, Ruby, Python, Go, Objective-C, C\#, CoffeeScript and Clojure.
      \item Have experience with the Spring Framework, the MEAN stack, JQuery, Android, iOs, and more.
      \item Have experience with Linux, Sublime Text, Atom, Eclipse, Visual Studio, Intellij, Git, Mercurial and more.
    \end{itemize}

    \section{Projects - More at \href{http://mpeterson2.github.io}{mpeterson2.github.io}}

      \project{Kanban}{https://github.com/mpeterson2/kanban}{
        Kanban is my senior thesis project at Carthage College. It is a single page web app written with the MEAN stack, meant for teams who want to use electronic Kanban boards.
      }

      \project{Turbo Wookie}{https://github.com/turbowookie/turbo-wookie}{
        Turbo Wookie is a collaborative jukebox; a group of people can start up a Turbo Wookie instance, share the address amongst themselves, and build a playlist that they'll be able to listen to concurrently.
      }

      \project{Save Session}{https://github.com/mpeterson2/save-session}{
        Save Session is a highly configurable package for the Atom text editor that remembers previous sessions. It automatically restores any files whether they is saved to disk or not, projects, window information and more.
      }
    \vspace{-2em}

\end{document}